%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
% COMPILE WITH xelatex MichaelPetersenCV.tex
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% some layout choices. 

% should we include citation numbers?
\newif\ifcitationnumbers
\citationnumbersfalse

% should this be a CV with a separate publication list, or without?
\newif\ifpublicationlist
\publicationlisttrue

% should we include all or select dynamics-relevant publications?
\newif\ifselectedpublications
\selectedpublicationsfalse

\documentclass[margin, a4paper,11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{times} % fallback font

\usepackage{hyperref}

\usepackage{url}

\setlength{\resumewidth}{4.7in} % Text width of the document

% https://www.overleaf.com/learn/latex/Using_colours_in_LaTeX
\usepackage[dvipsnames]{xcolor}
% now define a few colors to join webpage themes
\definecolor{blueshade}{RGB}{15, 29, 60}
\definecolor{redshade}{RGB}{172,54,56}
\definecolor{grey}{gray}{0.6}

% https://www.overleaf.com/learn/latex/Questions/I_have_a_custom_font_I%27d_like_to_load_to_my_document._How_can_I_do_this%3F
%steps to get the Roboto font: download the package from Google Fonts
% move the Regular, Italic, Bold fonts to the CV folder:
\usepackage{fontspec}
\setmainfont{Roboto}[Extension = .ttf, UprightFont = *-Regular, ItalicFont = *-Italic, BoldFont = *-Bold]

\begin{document}

\setlength{\parskip}{4pt}


\setlength{\sectionwidth}{1.5in}


%----------------------------------------------------------------------------------------
%	header
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\huge\bf \textcolor{blueshade}{Michael S. Petersen} }
\moveleft\hoffset\vbox{\color{grey}\hrule width 6.5in height 1pt}\smallskip
\moveleft.5\hoffset\centerline{Institute for Astronomy, University of Edinburgh, Royal Observatory}
\moveleft.5\hoffset\centerline{Blackford Hill, Edinburgh EH9 3HJ, UK}
\moveleft.5\hoffset\centerline{\textcolor{grey}{\href{mailto:michael.petersen@roe.ac.uk}{michael.petersen@roe.ac.uk}}}

\begin{resume}

\section{\sc \textcolor{redshade}{Research} }

Design, implement, execute, and analyse precision numerical models to understand dynamical evolution in disk galaxies and their halo environs.


\section{\sc \textcolor{redshade}{Position}}

{\bf Postdoctoral Research Associate,} working with Jorge Pe{\~n}arrubia. \hfill \textcolor{grey}{2019-}
% add name of consolidated grant case?

\section{\sc \textcolor{redshade}{Education}}

{\bf Doctor of Philosophy,} Astronomy \hfill \textcolor{grey}{2019}\\
\hspace*{0.25 in} {\sl \textcolor{blueshade}{The non-linear dynamics of barred galaxy evolution in $\Lambda$CDM}}\\
\hspace*{0.25 in} {\sl Advisors: Martin D. Weinberg, Neal Katz}\\
%\hspace*{0.4 in} Mary Dailey Irvine Grant \hfill \textcolor{grey}{2016, 2017, 2018}\\
%\hspace*{0.4 in} Massachusetts Space Grant \hfill 2010, 2011, 2015\\
{\bf Bachelor of Arts,} Astronomy \& Physics, Music \hfill \textcolor{grey}{2010}\\
\hspace*{0.25 in} {\sl Colgate University, Hamilton, NY}\\
\hspace*{0.4 in} Astronomy \& Physics Honors, Core Distinction

\section{\sc \textcolor{redshade}{Collaborations}}

{\bf Basis-function expansion (Beefy) Collaboration} \\
`Architect' status in a Center for Computational Astrophysics (NYC)-led collaboration (PIs: Kathryn Johnston [Columbia], Martin Weinberg [UMass]). The group is working to develop a holistic approach to galaxy evolution using basis function expansions.

{\bf SEGAL Collaboration} \\
Assisting analysis of bars in the New Horizon simulation within the SEGAL collaboration (PI: Christophe Pichon [IAP]). The group is working to develop a holistic approach to galaxy evolution using basis function expansions.

%{\bf Surrey-Edinburgh Streams Collaboration}\\


\section{\sc \textcolor{redshade}{Teaching \& Advising}}

{\bf University of Edinburgh MPhys Research Advisor} \hfill\textcolor{grey}{2020-}\\
Designed and advised a masters project at the University of Edinburgh.

{\bf University of Edinburgh Research Advisor} \hfill\textcolor{grey}{Summer 2020}\\
Designed, sought funding for, and advised two summer research projects for advanced undergraduate students at the University of Edinburgh.

% add titles of projects? and progress?
{\bf University of Edinburgh Senior Honours Research Advisor} \hfill\textcolor{grey}{2019-}\\
Designed and advised five research projects for undergraduate students
at the University of Edinburgh over three semesters.

{\bf Five College Astronomy Teaching Assistant} \hfill \textcolor{grey}{2014-2018}\\
Assisted Professor James Lowenthal, Dr. Anne Jaskot, and Dr. Kim Ward-Duong in Observational Techniques I/II, a two-semester observing course involving a yearly observational component at Kitt Peak National Observatory. University of Massachusetts Distinguished Teaching Award finalist.

%{\bf Research Mentor, 2016-2017}\\
%Mentored and advised Amelia Vinciguerra (UMass 2017) in her senior undergraduate research project in collaboration with Martin Weinberg.

\section{\sc \textcolor{redshade}{Service}}

{\bf Equality, Diversity and Inclusion Team Organiser} \hfill\textcolor{grey}{2020-}\\
Initiated a team to study issues of equality, diversity and inclusion at the Intitute for Astronomy.

{\bf ROE Seminar Organiser} \hfill\textcolor{grey}{2019-}\\
Responsible for selection of speakers and organising delivery of talks for the Royal Observatory. Includes remote organisation and hosting during work-from-home period.

{\bf Local Universe Reading Group Organiser} \hfill\textcolor{grey}{2019-}\\
Responsible for programming and hosting a roughly dozen-person reading group covering multiple research teams at the ROE.

%\section{\sc \textcolor{redshade}{Teaching}}

%{\bf Continuing Education Head Instructor} \hfill \textcolor{grey}{2013-2018}\\
%Developed a two-week intensive continuing education class for the University of Massachusetts, then reshaped the class into a program involving many graduate students.

%
%{\bf Public Outreach Lecturer, 2013-present}\\
%Advised the undergraduate Astronomy club. Lead semesterly star walks
%for dormitories. Offered yearly open night sky observing sessions.

%{\bf Python Instructor, 2014-present}\\
%Provided Python instruction and support to the undergraduate Five
%College summer undergraduate researchers.


\section{\sc \textcolor{redshade}{Recent Invited Talks}}
{\bf Institute of Astronomy (Cambridge) Dynamics Group}\hfill\textcolor{grey}{May 2020} \\
{\it Bar models beyond analytic formulae}

{\bf AIP Potsdam Local Universe Group} \hfill\textcolor{grey}{January 2020}\\
{\it Bespoke N-body experiments in barred galaxy dynamics}

{\bf University of St. Andrews} \hfill\textcolor{grey}{January 2020}\\
{\it Bespoke N-body experiments in barred galaxy dynamics}


%\section{\sc Selected Meetings \& Conferences}
%{\bf AAS 231, January 2018}, Washington, D.C.\\
%Dissertation: {\it A Modern Picture of Barred Galaxy Dynamics}

%{\bf APS April Meeting, January 2017}, Washington, D.C.\\
%Contributed Talk: {\it The Dynamical Response of Dark Matter to Galaxy Evolution Affects Direct-Detection Experiments}

%{\bf Great Lakes Cosmology Workshop, June 2016}, Hamilton, ON\\
%Contributed Talk: {\it Dark Matter Trapping by Stellar Bars: The Shadow Bar}

%{\bf What Shapes Galaxies?, April 2016}, STScI, Baltimore, MD\\
%Contributed Poster: {\it Dark Matter Trapping by Stellar Bars: The Shadow Bar}

%{\bf Structure and Dynamics of Disk Galaxies, August 2013}, Petit Jean Mountain, AR\\
%Contributed Talk: {\it Creation of Peanut-Shaped Bulges via the Slow Mode of Bar Growth}




\section{\sc \textcolor{redshade}{Selected Observational Experience}}

{\bf NASA IRTF}, Co-I (2018B, 2019B, 2020B), 12 nights\\
{\it SpeX+MORIS Star Spot Monitoring of K2 Selected T Tauri Stars in Taurus-Auriga}\\
{\it iSHELL Accretion and Gas Dynamics in Transition Disk-bearing Young Stars Across the Substellar Boundary}

{\bf KPNO 0.9m}, PI (2016-2017), 5 nights; Co-I (2014-2018), 30 nights\\
{\it Deep Imaging of Nearby Low Surface Brightness Disks}\\
{\it Ionization States of Green Pea Galaxies}
%Using the Half-Degree Imager (HDI).
% would be nice to put the Kim title in here as well

{\bf Large Millimeter Telescope}, PI (Early Science 2,3,4 2014-2016), 60 hours\\
{\it Circumstellar Disk Masses in IC~348}
%Using AzTEC, a 1.1 mm camera.


%{\bf Gemini South}, Co-I (2017A), 18 hours\\
%{\it High-Resolution Spectroscopy of Orbitally-Modulated Accretion Activity in Pre-Main Sequence Binaries.} Using PHOENIX.

%{\bf APO 3.5 m}, Co-I (2017B), 4 nights\\
%{\it Optical to near-infrared Monitoring of Eccentric Pre-Main
%  Sequence Binaries.} Using ECHELLE and TripleSpec.





\section{\sc \textcolor{redshade}{Professional Links}}
{\bf Research Webpage} \url{https://michael-petersen.github.io}

{\bf Github Code Repository} \url{https://github.com/michael-petersen}


\section{\sc \textcolor{redshade}{References}}

{\bf Jorge Pe{\~n}arrubia}\\
Postdoctoral Research Associate advisor.

{\bf Martin D. Weinberg}\\
Co-dissertation advisor.

{\bf Neal Katz}\\
Co-dissertation advisor.

\ifpublicationlist
\pagebreak
\input{Publications}
\fi

\end{resume}
\end{document}
% Local Variables:
% TeX-engine: xetex
% End:
