
% must have defined \selectedpublications. set up a check for if not defined?

% do some math to number the publications
% https://tex.stackexchange.com/questions/167222/perform-simple-calculations-on-user-defined-variables
\newcount\TotalPublications
\TotalPublications=7

\ifselectedpublications \advance\TotalPublications by -3\relax \fi

\newcount\PublicationsInReview
\PublicationsInReview=4


\section{\sc \textcolor{redshade}{Publications} }
 \underline{\sl Refereed Publications} \ifcitationnumbers  \textcolor{grey}{(Citations as of September 2020)} \fi \\
\the\TotalPublications.  {\bf \textcolor{blueshade}{Petersen, M. S.}} \& Pe{\~n}arrubia, J. \href{https://ui.adsabs.harvard.edu/abs/2020MNRAS.494L..11P/abstract}{\it Reflex motion in the Milky Way stellar halo resulting from the Large Magellanic Cloud infall}, 2020, MNRASL, 494:11. \ifcitationnumbers \textcolor{grey}{(10 citations)} \fi\\
\advance\TotalPublications by -1\relax
\the\TotalPublications.   {\bf \textcolor{blueshade}{Petersen, M. S.}}, Weinberg, M. D., and Katz, N. \href{https://ui.adsabs.harvard.edu/abs/2019MNRAS.490.3616P/abstract}{\it Using torque to understand barred galaxy models}, 2019, MNRAS, 490:3616. \ifcitationnumbers \textcolor{grey}{(2 citations)} \fi\\
\ifselectedpublications \else
\advance\TotalPublications by -1\relax
\the\TotalPublications.   {\bf \textcolor{blueshade}{Petersen, M. S.}}, Gutermuth, R.A.,  Nagel, E.,  Wilson, G.W., Lane, J. \href{https://ui.adsabs.harvard.edu/abs/2019MNRAS.488.1462P/abstract}{\it Early science with the Large Millimetre Telescope: new mm-wave detections of circumstellar discs in IC 348 from LMT/AzTEC}, 2019, MNRAS, 488:1462.\\ \fi
\advance\TotalPublications by -1\relax
\the\TotalPublications.   {\bf \textcolor{blueshade}{Petersen, M. S.}}, Katz, N. , \& Weinberg, M.D. \href{http://adsabs.harvard.edu/abs/2016PhRvD..94l3013P}{{\it The Dynamical Response of Dark Matter to Galaxy Evolution Affects Direct-Detection Experiments}}, Phys Rev D, 2016. Figure 4 was featured as part of the journal's \href{https://journals.aps.org/prd/kaleidoscope/prd/94/12/123013}{`Kaleidoscope'}. \ifcitationnumbers \textcolor{grey}{(7 citations)} \fi\\
\advance\TotalPublications by -1\relax
\the\TotalPublications.   {\bf \textcolor{blueshade}{Petersen, M. S.}}, Weinberg, M. D., and Katz, N. \href{http://adsabs.harvard.edu/abs/2016MNRAS.463.1952P}{\it
  Dark matter trapping by stellar bars: the shadow bar} 2016 MNRAS,
463:1952–1967. \ifcitationnumbers \textcolor{grey}{(13 citations)} \fi\\
\ifselectedpublications \else
\advance\TotalPublications by -1\relax
\the\TotalPublications.   Bary, Jeffrey S. \& {\bf \textcolor{blueshade}{Petersen, M. S.}}
\href{http://adsabs.harvard.edu/abs/2014ApJ...792...64B}{\it Anomalous
  Accretion Activity and the Spotted Nature of the DQ Tau Binary
  System} 2014 ApJ, 792:64. \ifcitationnumbers \textcolor{grey}{(14 citations)} \fi\\
\advance\TotalPublications by -1\relax
\the\TotalPublications.   Elmegreen, Debra M., and others including {\bf \textcolor{blueshade}{Petersen, M. S.}} \href{https://ui.adsabs.harvard.edu/abs/2009ApJ...701..306E/abstract}{\it Clumpy Galaxies in Goods and Gems: Massive Analogs of Local Dwarf Irregulars} 2009 ApJ, 701:306-329. \ifcitationnumbers \textcolor{grey}{(120 citations)} \fi\\ \fi

%\vspace*{8pt}
%\underline{\sl Conference Proceedings} \\
%{\bf Petersen, M. S.}, Weinberg, M. D., and Katz, N. \href{http://adsabs.harvard.edu/abs/2014ASPC..480..157P}{{\it 
%Creation of Peanut-Shaped Bulges via the Slow Mode of Bar Growth}} ASPC, 480:157.

\underline{\sl Publications In Review} \\
\the\PublicationsInReview.  Weinberg, M. D. \& {\bf \textcolor{blueshade}{Petersen, M. S.}} \href{https://arxiv.org/abs/2009.07870}{\it Using Multichannel Singular Spectrum Analysis to Study
  Galaxy Dynamics}, arXiv e-prints. \\
\advance\PublicationsInReview by -1\relax
\the\PublicationsInReview.  {\bf \textcolor{blueshade}{Petersen, M. S.}} \& Pe{\~n}arrubia, J.  \href{https://michael-petersen.github.io}{\it Detection of the Milky Way reflex motion induced by the Large Magellanic Cloud infall}\\
\advance\PublicationsInReview by -1\relax
\the\PublicationsInReview.  {\bf \textcolor{blueshade}{Petersen, M. S.}}, Weinberg, M. D., and Katz, N. \href{https://ui.adsabs.harvard.edu/abs/2019arXiv190205081P/abstract}{\it Using commensurabilities and orbit structure to understand barred galaxy evolution}, arXiv e-prints. \ifcitationnumbers \textcolor{grey}{(6 citations)} \fi\\
\advance\PublicationsInReview by -1\relax
\the\PublicationsInReview.  {\bf \textcolor{blueshade}{Petersen, M. S.}}, Weinberg, M. D., and Katz, N. \href{https://ui.adsabs.harvard.edu/abs/2019arXiv190308203P/abstract}{\it Using harmonic decomposition to understand barred galaxy evolution}, arXiv e-prints. \ifcitationnumbers \textcolor{grey}{(4 citations)} \fi\\

%\underline{\sl Publications To Be Submitted Before November 2020} \\
%1.  {\bf \textcolor{blueshade}{Petersen, M. S.}}, Weinberg, M. D., and Katz, N. %{\it Measuring the dynamical length of bars}, arXiv e-prints. \ifcitationnumbers \textcolor{grey}{(0 citations)} \fi
%2.  Reddish, J., Kraljic, K., and {\bf \textcolor{blueshade}{Petersen, M. S.}} %{\it A dearth of bars in the NewHorizons simulation}, arXiv e-prints. \ifcitationnumbers \textcolor{grey}{(0 citations)} \fi

%{\bf Petersen, M. S.}, Weinberg, M. D., and Katz, N. {\it Understanding trends in bar formation and evolution in varied $n$-body models} \\
%{\bf Petersen, M. S.}, Weinberg, M. D., and Katz, N. {\it Using the bar to drive radial mixing and bulge formation in a Milky Way-like galaxy} \\

